---
title: "5_Model_extensions"
author: "S. Jean"
date: "2023-08-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(dplyr)
library(tidyr)
library(stringi)
library(ggplot2)
library(here)

```


# I. Oligopoly extension
## A. Define functions

Define : 

-  `q_(x, N, M, ...)` : Cournot harvest with `N` traders and `M` farmers (in metric tons)

-  `cournot_harvest(x, ...)` : Cournot harvest with 1 trader and 1 farmer (in metric tons)

-  `monop_harvest(x, ...)`: Monopoly harvest (in metric tons)

-  `growth(x, ...)` : ogistic growth function, yields growth of population (in metric tons) 

```{r}
q_ = function(N,M,x,
             alpha_f. = alpha_f,
             alpha_w. = alpha_w, 
             beta_f. = beta_f,
             beta_w. = beta_w,
             gamma. = gamma,
             c. = c, 
             v. = v, 
             sigma. = sigma,
             W. = W){
  num = N*sigma.^2*x^2*(beta_f. * (M+1)*(alpha_w. - c.) - gamma.*M*(alpha_f.-v.))
  det = sigma.^2 * x^2 * (beta_f. * beta_w.* (N+1) * (M+1) - gamma.^2 * N * M) + 2*W*N*(M+1)*beta_f.
  y = num/det
  return(y)
}


cournot_harvest = function(x, 
                           alpha_f. = alpha_f, 
                           alpha_w. = alpha_w, 
                           beta_f. = beta_f, 
                           beta_w. = beta_w, 
                           gamma. = gamma, 
                           sigma. = sigma, 
                           c. = c, 
                           v. = v, 
                           W. = W_mid){
  y = ((sigma.^2)*(x^2)*(2*beta_f.*(alpha_w. - c.) - gamma.*(alpha_f. - v.)))/(4*beta_f.*W. + (sigma.^2)*(x^2)*(4*beta_f.*beta_w. - (gamma.^2)))
  return(y)
}

monop_harvest = function(x, 
                         alpha. = alpha, 
                         c. = c, 
                         sigma. = sigma, 
                         beta. = beta, 
                         W. = W_mid){
  y = ((alpha. - c.)*sigma.^2 * x^2) / (2*beta.* sigma.^2 * x^2 + 2*W.)
  return(y)
}

growth = function(x, 
                  k.=k, 
                  r.=r){
  y = r.*x*(1-x/k.)
  return(y)
}


```


## B. Set data for analysis

```{r, data & analysis}
# Load parameters
calibration = read.csv(here("data", 'outputs', "calibration_params.csv"))

for(i in 1:nrow(calibration)){
  assign(calibration$params[i], calibration$value[i])
}  


# Build the 2nd order parameters from parameter list
  # Differentiate parameters for Wild and Farmed inverse demands
alpha_w = alpha
alpha_f = alpha
beta_w = beta
beta_f = beta
  # Demand functions parameters
e   = gamma/(beta_w*beta_f - (gamma^2))
a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
b_f = beta_f/(beta_w*beta_f - (gamma^2))
b_w = beta_w/(beta_w*beta_f - (gamma^2))

W = W_mid
# set data : population
data = data.frame(x = seq(1,k))
x_ = seq(1,k)
data = data %>% 
  mutate("Monopoly" = monop_harvest(x_),
         #
         "1 trader - 1 farmer" = cournot_harvest(x_), 
         growth = growth(x_),
         '1 trader - 2 farmers' = q_(1,2,x_),
         '1 trader - 5 farmers' = q_(1, 5, x_),
         '1 trader - 10 farmers' = q_(1, 10, x_),
         '1 trader - 50 farmers' = q_(1, 50, x_),
         #
         '2 traders - 1 farmer' = q_(2, 1, x_),
         '2 traders - 2 farmers' = q_(2, 2, x_),
         '2 traders - 5 farmers'  = q_(2,5, x_),
         '2 traders - 10 farmers' = q_(2, 10, x_),
         '2 traders - 50 farmers' = q_(2, 50, x_),
         #
         '5 traders - 1 farmer' = q_(5, 1, x_),
         '5 traders - 2 farmers'  = q_(5, 2, x_),
         '5 traders - 5 farmers'  = q_(5,5,x_),
         '5 traders - 10 farmers' = q_(5,10, x_),
         '5 traders - 50 farmers' = q_(5, 50, x_),
         #
         '10 traders - 1 farmer' = q_(10, 1, x_),
         '10 traders - 2 farmers' = q_(10, 2, x_),
         '10 traders - 5 farmers' = q_(10, 5, x_),
         '10 traders - 10 farmers'= q_(10, 10, x_),
         '10 traders - 50 farmers'= q_(10, 50, x_),
         #
         '50 traders - 1 farmer' = q_(50, 1, x_),
         '50 traders - 2 farmers' = q_(50, 2, x_),
         '50 traders - 5 farmers' = q_(50, 5, x_),
         '50 traders - 10 farmers' = q_(50, 10, x_),
         '50 traders - 50 farmers' = q_(50, 50, x_))%>%
  pivot_longer(cols = -c('x'), # Set to long format for ggplot
              names_to = 'name', 
              values_to = 'values')%>%
  mutate(ss_ = values - growth(x))

levels(data$name) = c('Monopoly',
                      '1 trader - 1 farmer', 
                      '1 trader - 2 farmers',
                      '1 trader - 5 farmers',
                      '1 trader - 10 farmers',
                      '1 trader - 50 farmers',
                      #
                      '2 traders - 1 farmer',
                      "2 traders - 2 farmers",
                      '2 traders - 5 farmers',
                      '2 traders - 10 farmers',
                      '2 traders - 50 farmers',
                      #
                      '5 traders - 1 farmer', 
                      '5 traders - 2 farmers',
                      '5 traders - 5 farmers',
                      '5 traders - 10 farmers',
                      '5 traders - 50 farmers',
                      ###
                      "10 traders - 1 farmer",
                      '10 traders - 2 farmers',
                      '10 traders - 5 farmers',
                      '10 traders - 10 farmers',
                      '10 traders - 50 farmers',
                      #
                      '50 traders - 1 farmer',
                      '50 traders - 2 farmers',
                      '50 traders - 5 farmers',
                      '50 traders - 10 farmers',
                      '50 traders - 50 farmers')


data = data %>% mutate(name2 = sapply(strsplit(name, " - "), `[`, 1),
                       name3 = sapply(strsplit(name, " - "), `[`, 2))


# Smaller dataset 
data2 = data %>%
  subset(!(name %in% c('growth')))%>%
  filter(ss_ < .08 & ss_ > -.08)

# function to create the two groups : less trader or more trader
grouper = function(x){
  if(x %in% c('growth', 'Monopoly', '1 trader - 1 farmer')){
    return('Baseline')
  }else{ # Extract number of farmers and traders and compare them
    a = as.numeric(stri_extract_first_regex(strsplit(x, ' - ')[[1]][1], '[0-9]+'))
    b = as.numeric(stri_extract_first_regex(strsplit(x, ' - ')[[1]][2], '[0-9]+'))
    if(a < b){
      return('More farmers than traders')
    }else if(a >= b){
      return('More traders than farmers')
    }
  }
}

#

data2$grouper = sapply(data2$name, grouper)
data2$order = factor(paste0(data2$name, data2$grouper), c(paste0(levels(data2$name), 'Baseline'),
                                                          paste0(levels(data2$name), 'More farmers than traders'),
                                                          paste0(levels(data2$name), 'More traders than farmers')))


```

## C. Graphical output

```{r, graph1}
palette = c('paleturquoise3', 'steelblue1', 'royalblue1', 'mediumblue', 'navyblue')

monopoly_ss = data2 %>%
  subset(name == 'Monopoly')%>%
  select(x)%>%
  pull()

font_ =  'AppleGothic'

data2 %>%
  subset(!(grouper %in% c('Baseline')))%>%
  ggplot(aes(x = order, y = x, colour = name3, shape = name2))+
  facet_grid(~ grouper, scales = 'free')+
  geom_point()+
  geom_hline(yintercept =monopoly_ss, 
             linetype = "dashed")+
  #scale_x_discrete(limits = levels(data$name))+
  scale_x_discrete(breaks=data2$order, labels=data2$name)+
  #scale_colour_brewer()+
  scale_colour_manual(values = palette)+
  scale_shape_discrete()+
  theme_bw()+
  ylab('Steady state population')+
  xlab('')+
  guides(
    color = guide_legend(
      title = " ",  # Title for the first column
      ncol = 1              # Number of columns
    ),
    shape = guide_legend(
      title = " ",     # Title for the second column
      ncol = 1              # Number of columns
    )
  ) +
  theme(axis.text.x = element_text(angle = 70, 
                                   hjust = 1, 
                                   family = font_),
        axis.text.y = element_text(family = font_),
        axis.title.y = element_text(family = font_), 
        strip.text = element_text(family = font_),
        legend.position = 'right',
        legend.text = element_text(family = font_)
        )
```
```{r, graph2}

data2$name3 = as.factor(data2$name3)
levels(data2$name3) = c('1 farmer', '2 farmers', '5 farmers', '10 farmers', '50 farmers')

data2$name2 = as.factor(data2$name2)
levels(data2$name2) = c('1 trader', '2 traders', '5 traders', '10 traders', '50 traders', 'Monopoly')

data2$order2 = factor(paste0(data2$name3, data2$name2), c(paste0(levels(data2$name2), '1 farmer'),
                                                          paste0(levels(data2$name2), '2 farmer'),
                                                          paste0(levels(data2$name2), '5 farmer'),
                                                          paste0(levels(data2$name2), '10 farmer'),
                                                          paste0(levels(data2$name2), '50 farmer')))

data2 %>%
  subset(!(name %in% c('Monopoly')))%>%
  ggplot(aes(x = order2, y = x, colour = name3))+
  facet_grid(~ name2, scales = 'free')+
  geom_point()+
  geom_hline(yintercept =monopoly_ss, 
             linetype = "dashed")+
  #scale_x_discrete(limits = levels(data$name))+
  scale_x_discrete(breaks=data2$order2, labels=data2$name2)+
  #scale_colour_brewer(palette = 'GnBu')+
  scale_colour_manual(values = palette)+
  theme_bw()+
  guides(
    color = guide_legend(
      title = " ",  # Title for the first column
      ncol = 1              # Number of columns
  ))+
  ylab('Steady state population')+
  xlab('')+
  theme(axis.text.x = element_text(angle = 70, 
                                   hjust = 1, 
                                   family = font_),
        axis.text.y = element_text(family = font_),
        axis.title.y = element_text(family = font_), 
        strip.text = element_text(family = font_),
        legend.position = 'right',
        legend.text = element_text(family = font_)
        )

```

# II. Extended cartel model 
In this section, we investigate the effect of a 'vertical monopoly' take over the aquaculture facility. See supplementary materials section ??? for derivation and discussions. 
## A. Define harvest
```{r, extended cartel}
q_w = function(x,
               alpha_f. = alpha_f, 
               alpha_w. = alpha_w, 
               beta_f.  = beta_f, 
               beta_w.  = beta_w, 
               gamma.   = gamma, 
               W.       = W_mid,
               c.       = c,
               v.       = v,
               sigma.   = sigma){
  num = sigma.^2 * x^2 * (beta_f.*(alpha_w. - c.) - gamma.*(alpha_f. - v.))
  den = 2*(beta_f.*W. + sigma.^2 * x^2 *(beta_f. * beta_w. - gamma.^2))
  y = num/den
  return(y)
}

```

## B. Run scenario

```{r, extended cartel run}
x_ = seq(1,k)
data = data.frame(x = x_)
data = data %>%
  mutate(Growth = growth(x_),
         'Vertical Monopoly' = monop_harvest(x_),
         Cournot = cournot_harvest(x_),
         'Cartel takeover' = q_w(x_))%>%
  pivot_longer(cols = -c('x'),
               names_to = 'name',
               values_to = 'values')

```

## C. Graphical output
```{r, extended cartel graph}
data %>%
  ggplot(aes(x = x, y = values, color = name))+
  geom_line()+
  guides(
    color = guide_legend(
      title = " ",  # Title for the first column
      ncol = 1              # Number of columns
    ),
    shape = guide_legend(
      title = " ",     # Title for the second column
      ncol = 1              # Number of columns
    )
  ) +
  scale_color_manual(values = c('purple', 'lightgreen','black', 'forestgreen'))+
  scale_linetype_manual(values = c("solid", "solid",'solid', 'dotted' )) +
  ylab('Growth / Harvest')+
  xlab('Population')+  
  theme_bw()+
  theme(axis.text.x = element_text(angle = 70, 
                                   hjust = 1, 
                                   family = font_),
        axis.title.x = element_text(family = font_),
        axis.text.y = element_text(family = font_),
        axis.title.y = element_text(family = font_), 
        strip.text = element_text(family = font_),
        legend.position = 'right',
        legend.text = element_text(family = font_)
        )
  ggsave(here("visuals", "Figure_cartel_takeover.jpg"))

```
