---
title: "Parameters"
author: "Lawson et al."
date: "2023-06-16"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
options(scipen=999)

#rm(list = ls())

library(tidyverse)
library("ggsci")
library(here)
library(knitr)
library(stargazer)

#if(!(all(c('Fishlife', 'devtools') %in% installed.packages()))){
#  install.packages('devtools')
#  devtools::install_github("james-thorson/FishLife")
#}

library(FishLife)
library(kableExtra)

Latex =T
```

In this script, we share the code to replicate our parameters.

# 0. File architecture

This still needs to be amended once we have finished all of the architecture in the final repo. 

```{r}
if(dir.exists(paste0(getwd(),"/scripts/"))==F){
  dir.create(paste0(getwd(),'/scripts/'))
}
if(dir.exists(paste0(getwd(),'/visuals/'))==F){
  dir.create(paste0(getwd(),'/visuals/'))
  dir.create(paste0(getwd(),'/visuals/supplementary_visuals/'))
}
```

# I. Load data

* `dat_p.csv` : price & quantity data from seizures (Source: collated by the Environmental Investigation Agency (EIA) and processed for analysis by authors).

* `totoaba_biomass_catch_20230516.csv` : historical biomass and catch (Source: INAPESCA 2020).

* `w_par.csv`: cost data from for poaching costs (see Supplementary Materials).

* `v_par.csv`: cost data from for aquaculture costs (see Supplementary Materials).

```{r, Load data}
dat_p = read.csv(here("data","inputs","dat_p.csv")) #Price-quantity data (OG Paper)
dat_p = dat_p %>%
  mutate(price_buche = g*p,
         price_kg = p*1000, 
         price_buche_kg = price_buche*1000)


dat_b = read.csv(here('data', 'inputs', "totoaba_biomass_catch_20230516.csv")) %>% 
  rename(y = X) %>% 
  rename(b = Biomass..Tonnes.) %>% 
  rename(c = Catch..Tonnes.)

w_par = read.csv(here("data", 'inputs', "w_par.csv"))
v_par = read.csv(here("data", 'inputs', "v_par.csv")) 

sources = read.csv(here("data", 'inputs', "sources.csv"))

```


# II. Demand

```{r, Demand}
avg_toto_weight = 25.7
avg_buche_weight = .5

buche_to_toto = avg_buche_weight/avg_toto_weight

# Merge observed price data with observed catch and biomass data from 2013 to 2017
new_dat = merge(dat_b %>%
                  subset(y>2013) %>% 
                  select(y,
                         c)%>%
                  rename(year=y), 
                dat_p %>% 
                  select(year, 
                         price_kg))%>%
  mutate(price_ton = price_kg * 1000, 
         price_ton_toto = price_ton * buche_to_toto)

# Graphical output
new_dat %>%
  ggplot(aes(x = c, y = price_ton_toto))+
  geom_point(aes(colour = as.factor(year)), size = 3)+
  geom_smooth(method = 'lm', colour = 'black')+
  theme_bw()+
  theme(legend.position = 'bottom')+
  xlab('Catch')+
  ylab('Price per ton of totoaba in USD')+
  scale_color_aaas()+
  labs(colour = NULL)
ggsave(here('visuals','supplementary_visuals','demand_data.jpg' ))
# Model
model  = lm(price_ton_toto ~ c, data = new_dat)
summary(model)

# Coefficients
alpha = model$coefficients[1]
beta = -model$coefficients[2]
gamma = 0.9*beta

```


# II. Biological parameters
```{r, Biological}
# Totoaba macdonaldi is in FishLife database, so prediction for 'r' is informed by species-specific data.
Predict = Plot_taxa(Search_species(Genus="Totoaba",Species="macdonaldi")$match_taxonomy, mfrow=c(2,2))

Predict[[1]]$Mean_pred %>%
  kbl() %>%
  kable_styling()

r = Predict[[1]]$Mean_pred['r']


k <- 20226 #carrying capacity (biomass in mt) (source: INAPESCA 2020) 

# Catchability : catch per trip and stock
max_E = sum(w_par$total_fleet_days_year)

catchability = dat_b %>% 
  subset(y==2016) %>% 
  select(c)/(max_E *dat_b %>% subset(y==2016) %>% select(b))
catchability = pull(catchability)
```

# III. Poaching costs


## A. Calculate W

```{r calculating cost of poaching}

# W parameter, proportional increase in cost per unit (trip)

#Step one, get all annual operating costs
# Goal is to calculate cost per vessel trip (we have total fleet days per year which is number of vessels * fishing days per month)
# First calculate total annual costs for the entire fleet

w_par_ops <- w_par %>% 
  mutate(cost_crew_earnings = (totoaba_year * price_fishers_per_totoaba * monthly_earnings_paid)) %>% 
  mutate(cost_food_fuel = (foodfuel_day * total_fleet_days_year)) %>% 
  mutate(cost_gear = total_fleet_days_year*(gear_loss_day*gear_replacement)) %>% 
  mutate(revenue_per_month = (totoaba_year*(price_fishers_per_totoaba)) - (cost_crew_earnings-cost_food_fuel-cost_gear))

# Next, divide by total fishing days per year

w_par_val <- w_par_ops %>% 
  select(vessels, totoaba_day, total_fleet_days_year,cost_crew_earnings,cost_food_fuel,cost_gear,bribes_year,revenue_per_month) %>% 
  mutate(cost_per_trip = (cost_crew_earnings + cost_food_fuel + cost_gear + bribes_year)/total_fleet_days_year) 

#Adding in gear and vessel confiscation (calculated as a shared cost applied to the entire fleet)

w_pal_val_conf <- w_par_val %>%
  add_column(net_confs_cost_fleetday=664000/1920) %>% #Total cost as a proportion of reported confiscations averaged over the year (1,920 fishing trips total). 5,720 nets in the water each year (each vessel sets 2-3 nets), and 0.07 of those nets are confiscated (we know that there are 415 gear confiscation events each year). So if we assume that each net costs $1,600, then our total cost to the fleet is $664,000.
  add_column(vessel_confs_cost_fleetday=1230000/1920) %>% #Total cost as a proportion of reported vessel seizures averaged over the year (1,920 fishing trips total). There are 150 boats in total each year, and 0.546 are confiscated (there are 82 confiscations a year). So we assume each boat is worth $15,000, and therefore the total cost to the fleet is $1,230,000.
  add_column(fines_cost_fleetday=81675/1920) %>% #Total cost as a proportion of reported vessel seizures averaged over the year (1,920 fishing trips total). There are 11 arrests/convictions where people are fined $7,425/event, which would add an additional cost of $42.54.
  mutate(cost_per_trip = (cost_crew_earnings + cost_food_fuel + cost_gear + bribes_year)/total_fleet_days_year) %>% 
  mutate(cost_per_trip_wconf = cost_per_trip + net_confs_cost_fleetday + vessel_confs_cost_fleetday + fines_cost_fleetday)

costs = w_pal_val_conf %>% 
  select(cost_per_trip_wconf)%>%
  unique()%>%
  drop_na()%>%
  pull()%>%
  sort()
# Final estimates of cost per trip (W)

W_low = costs[1] #Low Season 
W_mid = costs[2] # Mid Season
W_high = costs[3] # High Season
```

## B. Export data and sources for W

```{r supplementary materials tables}
classer = function(x){
  if(x %in% c(1,6)){
    return('Low')
  }else if(x %in% c(2,5)){
    return('Mid')
  }else if(x %in% c(3,4)){
    return('High')
  }
}
#w_par_b = w_pal_val_conf %>% 
w_par_b = w_par %>% 
  mutate(month = seq(1:nrow(w_pal_val_conf)))%>%
    subset(vessels>0)%>%
  mutate(season = sapply(month, classer))%>%
  group_by(season)%>%
  summarise(across(everything(),mean),
            .groups= 'drop')%>%
  t()%>%
  as.data.frame()

w_par_b = w_par_b%>%
  mutate(name = rownames(w_par_b))

sources_w = sources %>% 
  subset(parameter=='W') %>% 
  select(-parameter)

w_par_b = merge(w_par_b, sources_w, by = 'name', all=T)

colnames(w_par_b) = c('Variable', 'High', 'Low', 'Mid', 'Source')

order__ = c('vessels', 'days permonth', 'total fleet days year', 'foodfuel day', 'totoaba gearset', 'gear loss day', 'gearset vessel perday', 'gear replacement', 'bribes year', 'Average cost')

w_par_b = w_par_b %>% 
  drop_na()%>%
  rbind(append('Average cost', append(round(costs,2), 'Own comp' )))%>%
  subset(!(Variable %in% c('crew_size','month', 'monthly_earnings_paid', 'price_fishers_per_totoaba',
                           'totoaba_year')))%>%
  mutate(Variable = str_replace_all(Variable, '_', ' '), 
         Source = replace(Source, Source == 'INAPESCA 2020', 'cite{INAPESCA}'))%>%
  arrange(match(Variable, order__))%>%
  relocate(Variable, Low, Mid, High, Source)


if(Latex==T){
  w_par_b %>%
    kable(caption ='Information supporting $W$' ,
          format = 'latex', 
          align = 'c')
}
```


Find the parameter $W_{quad}$ such that :
$$
TotCost(E)=WE^2 \Rightarrow MargCost(E) = 2W_{quad}E
$$

And 

$$
MargCost(E_{hist}) = AvgCost(E_{hist})\Rightarrow W_{quad} = \frac{W_{avg}}{2E_{hist}}
$$

```{r, Quadratic costs}
W_qlow = W_low/(2*max_E)
W_qmid = W_mid/(2*max_E)
W_qhigh = W_high/(2*max_E)

# Recover fixed cost parameter
cost_ = data.frame(trips = seq(1,1.5*max_E))%>%
  mutate(trips2 = trips^2,
         low = W_low*trips, 
         mid = W_mid*trips,
         high = W_high*trips,
         sq_low = W_qlow*trips2,
         sq_mid = W_qmid*trips2,
         sq_high = W_qhigh*trips2)

cost_ %>%
  ggplot(aes(x = trips))+
  geom_line(aes(y = low, colour = 'low'))+
  geom_line(aes(y = mid, colour = 'mid'))+
  geom_line(aes(y = high, colour = 'high'))+
  geom_line(aes(y = sq_low, colour = 'low'))+
  geom_line(aes(y = sq_mid, colour = 'mid'))+
  geom_line(aes(y = sq_high, colour = 'high'))+
  scale_colour_manual(values = c( 'red','black','grey', 'red', 'black','grey'))+
  theme_bw()+
  ylab('Cost')+
  labs(colour = ' ')

fixed_low = W_low*max_E - W_qlow*(max_E^2)
fixed_mid = W_mid*max_E - W_qmid*(max_E^2)
fixed_high = W_high*max_E - W_qhigh*(max_E^2)
```


# IV. Trading costs

```{r trading costs}
c = 0
```
We use `c=` `r c` as trading costs.

# V. Farming costs

```{r calculating cost of farming}

# Farming cost data, from Buche Bros

# Final estimate per tonne of totoaba per year:
v_ = v_par %>% 
  select(op_cost_per_t)%>%
  pull()
age = 4.5
v = v_*age
# Calculating size at harvest
aqua_par_w <- read.csv(here("data", 'inputs', "aqua_par_wild.csv"))
aqua_par_f <- read.csv(here("data", 'inputs', "aqua_par_farm.csv"))
```
At 4.5 years under farming conditions, a totoaba should have a `r aqua_par_f %>% subset(Totoaba_Age==4.5) %>% select(Weight_Buche_g) %>% pull() %>% round(2)`g swim bladder. At 5 years under farming conditions, a totoaba should have a `r aqua_par_f %>% subset(Totoaba_Age==5) %>% select(Weight_Buche_g) %>% pull() %>% round(2)` g swim bladder

```{r table for v}

v_par_b = v_par %>% 
  t() %>% 
  as.data.frame()
v_par_b = v_par_b %>%
  mutate(name = rownames(v_par_b))

order__ = rownames(v_par_b)

sources_v = sources %>% 
  subset(parameter=='v') %>% 
  select(-parameter)

v_par_b = merge(v_par_b, sources_v, by='name',  all = T)%>%
  arrange(match(name, order__))%>%
  mutate(name = str_replace_all(name, '_', ' '))
if(Latex==T){
  v_par_b %>%
    kable(caption ='Information supporting $v$' ,
          format = 'latex', 
          align = 'c')
}
```


# VI. Save calibration data
```{r}
params = c('alpha', 'beta', 'r', 'k', 'sigma', 'W_mid', 'W_low', 'W_high', 'avg_cost', 'age', 'gamma', 'v', 'c')
value = c(alpha, beta, r, k, catchability, W_qmid, W_qlow, W_qhigh, W_mid, age, gamma, v, c)
concept = c('Demand model : intercept', 
            'Demand model : coefficient', 
            'Intrinsic growth rate', 
            'Carrying capacity (in metric tons)',
            'Catchability', 
            'Parameter cost (MC = Avg) at historical value - middle', 
            'Parameter cost (MC = Avg) at historical value - low', 
            'Parameter cost (MC = Avg) at historical value - high', 
            'Average cost per vessel trip', 
            'Age of farmed totoaba', 
            'Substitutability', 
            'Unit cost of farming', 
            'Unit cost of trading')

units = c('USD', 'USD/metric ton of biomass', 'unitless',  '% of biomass/vessel trip', 'metric tons of biomass', 'USD',  'USD', 'USD', 'USD', 'Years', 'Unitless', 'USD/metric ton of biomass', 'USD/ metric ton of biomass')

calibration = data.frame(params, value, concept, units)
write.csv(calibration, here('data', 'outputs', 'calibration_params.csv'))
```

```{r, calibration2}
calibration %>%  
  mutate(value = round(value, 2))%>%
  kbl() %>%
  kable_styling()

Latex = T

if(Latex==T){
  calibration %>%
    mutate(value = round(value, 2))%>%
    kable(caption = 'Parameters for calibration', 
          format = 'latex', 
          align = 'c')%>%
    kable_minimal(full_width = F)
}
```


