---
title: "2b_Additional module"
author: "Lawson et al"
date: "2023-07-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

options(scipen=999)

library(tidyverse)
library("ggsci")
library(here)
library(knitr)
library(stargazer)
library(khroma)
rm(list = ls())
```

## Modify original model to include other counterfactuals

```{r, load results}

result1 = read.csv(here('data', 'outputs', 'result1.csv'))
calibration = read.csv(here("data", 'outputs', "calibration_params.csv"))

for(i in 1:nrow(calibration)){
  assign(calibration$params[i], calibration$value[i])
}  
```

### Include Open Access equilibrium

Using equation 3 in Section 2.1 of the Supplementary materials : 

```{r, open access}
open_access = function(x, alpha_ = alpha, sigma_ = sigma, W_ = W_mid, beta_ = beta, c_ = c){
  y = ((alpha_ - c_)*sigma_^2*x^2)/(2*W_ + beta_*sigma_^2*x^2)
  return(y)
}
result1 = result1 %>% mutate(open_access = open_access(x))
```

### Include Harvest when there is aquaculture, and there is a price taking trader

```{r, aquaculture & trader}
result1 = result1 %>%
  mutate(comp_aqua = (v-c)*sigma^2*x^2/(4*W_mid))
```

### Include harvest when there is aquaculture and open access
```{r, aquaculture & oa}
result1 = result1 %>%
  mutate(oa_aqua = (v-c)*sigma^2*x^2/(2*W_mid))
```

## Graphical outputs
```{r, data processing}
for_graph = result1 %>%
  select(x,
         growth, 
         pt_harvest, 
         comp_aqua,
         monop_harvest, 
         cournot_harvest, 
         bertrand_harvest, 
         open_access,
         oa_aqua
         )%>%
  pivot_longer(cols = -c(x),
               names_to = 'names',
               values_to = 'values')

set1 = function(x){
  if(x %in% c('monop_harvest', 'open_access', 'pt_harvest')){
    return('Baseline')
  }else if(x == 'growth'){
    return('Baseline')
  }else{
    return('With aquaculture')
  }
}

set2 = function(x){
  if(x %in% c('pt_harvest', 'comp_aqua')){
    return('Competitive end market')
  }else if(x %in% c('monop_harvest', 'cournot_harvest', 'bertrand_harvest')){
    return('Cartel controls upstream and downstream')
  }else if(x %in% c('oa_aqua', 'open_access')){
    return('Open access')
  }else{
    return('Growth')
  }
}
  
for_graph = for_graph %>%
  mutate(set1 = sapply(names, set1), 
         set2 = sapply(names, set2))

```


<<<<<<< HEAD
```{r, graphs}
=======
```{r graphs}
>>>>>>> 2d33c316e982831d57fe509ce690f1aa784de6be

color1 = 'red'
color2 = 'blue'
color3 = 'seagreen3'

for_graph %>%
  ggplot(aes(x=x, y= values, colour = names))+
  geom_line()

## Both graphs present baseline and post policy outcomes
for_graph %>%
  filter(set1 == 'baseline' | names == 'growth')%>%
  ggplot(aes(x=x, y= values, colour= names))+
  geom_line(linewidth = 1)+
  theme_bw()+
  scale_color_manual(values = c('black', color1, color2, color3))

for_graph %>%
  filter(set1 == 'After policy' | names == 'growth')%>%
   ggplot(aes(x=x, y= values, colour= names))+
  geom_line()+
  theme_bw()+
  scale_color_manual(values = c(color1, color3, color1,'black', color2 ))

result1 %>%
  ggplot(aes(x = x))+
  geom_line(aes(y = growth), linewidth = 1)+
  geom_line(aes(y = monop_harvest, colour = 'Monopoly'), linewidth = 1)+
  geom_line(aes(y = cournot_harvest, colour = 'Cournot'), linetype = 2, linewidth  =1 )+
  geom_line(aes(y = bertrand_harvest, colour = 'Betrand'), linetype = 4, linewidth = 1)+
  theme_bw()+
  scale_color_manual(values = c(color1, color1, color1))


# Baseline graph : 
result1 %>%
  ggplot(aes(x = x))+
  geom_line(aes(y = growth), linewidth = 1)+
  geom_line(aes(y = monop_harvest, colour = 'Trader has full control over markets'), linewidth = 1)+
  geom_line(aes(y = open_access, colour = 'Open access fishery'), linewidth = 1)+
  geom_line(aes(y = pt_harvest, colour = 'Trader sells on competitive market'), linewidth = 1)+
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  labs(colour = ' ')+
  theme(legend.position = 'bottom')+
  scale_color_manual(values = c(color1, color2, color3, 'black'))

# After graph
result1 %>%
  ggplot(aes(x = x))+
  geom_line(aes(y = growth), linewidth = 1)+
  geom_line(aes(y = cournot_harvest, colour = 'Trader competes in quantity '), linewidth = 1)+
  geom_line(aes(y = bertrand_harvest, colour = 'Trader competes in prices'), linewidth = 1)+
  geom_line(aes(y = comp_aqua, colour = 'Trader competes on competitive market'), linewidth = 1)+
    geom_line(aes(y = oa_aqua, colour = 'Open access fishery competes on competitive market'), linewidth = 1)+
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  ylim(0,1250)+
  labs(colour = ' ')+
  guides(color=guide_legend(nrow=2,byrow=TRUE))+
  theme(legend.position = 'bottom')+
  scale_color_manual(values = c(color1, color2, color2, color3, 'black'))

# By market structure
  result1 %>%
    ggplot(aes(x = x))+
    geom_line(aes(y = growth), linewidth = 1)+
    geom_line(aes(y = cournot_harvest, colour = 'Trader competes in quantity '), linetype = 4, linewidth = 1)+
    geom_line(aes(y = bertrand_harvest, colour = 'Trader competes in prices'),linetype = 2, linewidth = 1)+
  geom_line(aes(y = monop_harvest, colour = 'Trader has full market control'), linewidth = 1)+
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  labs(colour = ' ')+
  guides(color=guide_legend(nrow=2,byrow=TRUE))+
  theme(legend.position = 'bottom')+
  scale_color_manual(values = c('darkblue','turquoise', color2, 'black'))
  
  result1 %>%
    ggplot(aes(x = x))+
    geom_line(aes(y = growth), linewidth = 1)+
    geom_line(aes(y = open_access, colour = 'Open access fishery'), linewidth = 1)+
    geom_line(aes(y = oa_aqua, colour = 'Open access fishery competes with aquaculture on competitive market'), linewidth = 1)+
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  labs(colour = ' ')+
  guides(color=guide_legend(nrow=2,byrow=TRUE))+
  theme(legend.position = 'bottom')+
  scale_color_manual(values = c(color1,'orange', 'black'))
  
  result1 %>%
    ggplot(aes(x = x))+
    geom_line(aes(y = growth), linewidth = 1)+
    geom_line(aes(y = pt_harvest, colour = 'Trader operates on competitive market'), linewidth = 1)+
    geom_line(aes(y = oa_aqua, colour = 'Trader competes with aquaculture on competitive market'), linewidth = 1)+
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  labs(colour = ' ')+
  guides(color=guide_legend(nrow=2,byrow=TRUE))+
  theme(legend.position = 'bottom')+
  scale_color_manual(values = c(color3, 'springgreen', 'black'))

```

```{r final graphs}


result1 %>%
  ggplot(aes(x = x))+
  theme_bw()+
  geom_line(aes(y = growth), linewidth = 1, color = 'black') +
  geom_line(aes(y = open_access), linewidth = 1, color='blue') +
  geom_line(aes(y = monop_harvest), linewidth = 1, color='red') +
  geom_line(aes(y = cournot_harvest), linewidth  = 1, colour = 'green') +
  geom_line(aes(y = bertrand_harvest), linewidth = 1, colour = 'pink') +
  scale_linetype_manual(breaks = c("growth", "open_access", "monop_harvest", "cournot_harvest", "bertrand_harvest"),
                        values = c("growth"=1, "open_access"=1, "monop_harvest"=2, "cournot_harvest"=2, "bertrand_harvest"=2))


```
```{r}
for_graph$set1 = as.factor(unlist(for_graph$set1))
for_graph$set2 = as.factor(unlist(for_graph$set2))

font_ = 'AppleGothic'

plot_ = for_graph %>%
  #subset(names != 'growth')%>%
  ggplot(aes(x = x, 
             y = values, 
             color = set2, 
             group = names,
             linetype = set1)) +
  geom_line(size = 0.7) +  # Use geom_line instead of geom_point
  
  # Set the linetype scale for different linestyles
  scale_linetype_manual(values = c("dotted", "solid", "solid")) +
  
  # Customize the legend
  guides(
    color = guide_legend(
      title = " ",  # Title for the first column
      ncol = 2              # Number of columns
    ),
    linetype = guide_legend(
      title = " ",     # Title for the second column
      ncol = 1              # Number of columns
    )
  ) +
  ylim(0,1250)+
  # Move the legend to the bottom
  theme_bw()+
  ylab('Growth / harvest')+
  xlab('Population stock')+
  theme(legend.position = "bottom",
        axis.title.x  = element_text(family = font_),
        axis.title.y  = element_text(family = font_),
        legend.text = element_text(family = font_))+
  scale_color_manual(values = c('firebrick3','#1f78b4', 'black','forestgreen') )


plot_ + annotate("text", x = c(20000,20000), y = c(400,600), 
         label =  c("Quantity setting", "Price setting"), color="firebrick3", 
         size=2 , angle=0, fontface="italic")

```


```{r}
checker = store %>%
  subset(spec %in% c('alpha', 'baseline'))

ss_baseline = checker %>% subset(spec == 'baseline') %>% select(ss_monop1) %>% pull()
to_keep = c('alpha','ss_monop1', 'ss_monop3', 'ss_cournot1', 'ss_bertrand1', 'ss_bertrand1_norm', 'ss_cournot1_norm', 'transformation')

output2 = function(x){
  if(x =='ss_cournot1_norm'){
    return('Cournot steady state - normalized (in %)')
  }else if(x == 'ss_bertrand1_norm'){
    return('Bertrand steady state - normalized (in %)')
  }
}

checker = checker %>%
  mutate(ss_cournot1_norm = (ss_cournot1/ss_baseline -1)*100, 
         ss_bertrand1_norm = (ss_bertrand1/ss_baseline -1)*100)%>% 
  select(all_of(to_keep))

checker = checker%>%
  pivot_longer(cols = !c('alpha', 'transformation'),
               values_to = 'values', 
               names_to = 'variables') %>%
  subset(transformation >=1)

checker %>% 
  subset(variables %in% c('ss_cournot1_norm', 'ss_bertrand1_norm')) %>%
  mutate(variables  = sapply(variables,output2))%>%
  ggplot(aes(x=transformation))+
  geom_point(aes(y = values, colour = variables ), size=2)+
  theme_bw()+
  geom_hline(yintercept = 0)+
  scale_colour_aaas()
ggsave(here('visuals/supplementary_visuals', 'Figure7.png'))
```