---
title: "Sensitivity analysis"
author: "Lawson et al"
date: "2023-06-20"
output: html_document
---

# Sensitivity analysis

```{r setup, include = F}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(scales)
library(colorspace)
library("ggsci")
library(here)
library(knitr)
library(stargazer)
library(parallel)
library(wesanderson)

#rm(list = ls())
```


## A. Load parameters for baseline

```{r}

calibration = read.csv(here('data', 'outputs', 'calibration_params.csv'))

for(i in 1:nrow(calibration)){
  assign(calibration$params[i], calibration$value[i])
}
```

## B. Define the parameters for sensitivity analysis

For this version of the sensitivity analysis, I generate combinations based only on 1 variable being different. This may make more sense. The sensitivity analysis is ran for cost and demand data. Other variables can be included, and other values can be included. 

```{r}
# Sensitivity analysis around v, gamma, alpha, W, c

# I. Get a baseline dataframe with all the parameters we may want to test. ####

# It is a dataframe because it includes a lot of possible values for v and gamma

baseline = data.frame(beta = beta, 
                      alpha = alpha, 
                      gamma = gamma, 
                      W = W_mid, 
                      c = c,
                      v = v,
                      r = r, 
                      k = k,
                      sigma = sigma,
                      spec = 'baseline', 
                      transformation = 1)

params_sensitivity = baseline

# II. Define all the parameter values we want to test: ####
# Important : define those values as COEFFICIENTS to be applied to the variables
# Little sloppy, but the idea is to make sure all vectors are the same length
# for storage in dataframe
v_sens = c( 0.05, .1, .5, .6, .7, .8, 1.2, 1.5)
gamma_sens = c(0.0001, .01, .1/gamma*beta, .2/gamma*beta, .5/gamma*beta, .8/gamma*beta, .95/gamma*beta, .9999/gamma*beta)
c_sens = c(0, 2,  5, 8, 10, 15, 20, 50)
alpha_sens = c(.5, .6, .8, 1.2, 1.4, 1.6, 1.8, 2)
W_sens = c(W_low/W_mid,W_high/W_mid, 2, 4, 6, NA, NA, NA)
beta_sens = c(.5, .8, 1.2, 1.5, 1.8, 2, NA, NA)
# Store into data.frame
sensitivity_values = data.frame()%>%
  rbind(v_sens, gamma_sens, c_sens, alpha_sens, W_sens, beta_sens)
sensitivity_values = cbind(data.frame(c('v', 'gamma', 'c', 'alpha', 'W', 'beta')),
                           sensitivity_values)

colnames(sensitivity_values) = append(c('var'), c(paste0('val',1:length(W_sens))))

# III. Loop to get the data we want ####
# Here, loop over names.
for(name in sensitivity_values$var){
  dat = baseline
  to_mult = sensitivity_values %>% subset(var==name) %>% select(-var)%>% unlist()
  # Take all the values that are non NA we want to transform baseline data with
  to_mult = to_mult[!is.na(to_mult)]

  # Loop over each value : store data with (i) what variable is modified and
  # (ii) the values we apply to them
  for (val in to_mult){
    
    dat = baseline
  
    idea= as.name(name)
    dat[[idea]] = dat%>%
      select(all_of(idea))%>%
      unlist()*val
    dat$spec = paste(name)
    dat$transformation = val
    params_sensitivity = rbind(params_sensitivity, dat)
  }
}

# c and v together
c_sens = seq(0.1, 15000, by = 100)
v_sens = seq(0.1,1.5, by = .05)*v
a = expand_grid(c_sens, v_sens)
colnames(a) = c('c', 'v')

a = cbind(baseline %>% select(-c('c', 'v', 'spec', 'transformation'))%>% slice(rep(1:n(), each = nrow(a))), a)

a = a %>% mutate(spec = 'c and v', 
                 transformation = paste(c,' and ', v))

params_sensitivity = rbind(params_sensitivity, a)

# c, v, and gamma together
c_sens = seq(0.1, 8, by = .2)*c
v_sens = seq(0.1,1.5, by = .2)*v
gamma_sens = seq(.1, .9, by = .1)*beta
a = expand_grid(c_sens, v_sens, gamma_sens)
colnames(a) = c('c', 'v',"gamma")
a = cbind(baseline %>% select(-c('c', 'v', 'gamma', 'spec', 'transformation'))%>% slice(rep(1:n(), each = nrow(a))), a)
a = a %>% mutate(spec = 'c and v and gamma', 
                 transformation = paste(c,' and ', v, 'and', gamma))
params_sensitivity = rbind(params_sensitivity, a)

#alpha and gamma together
alpha_sens = seq(0.8,2,.2)*alpha
gamma_sens = seq(.1, .95, by = .05)*beta
a = expand_grid(alpha_sens, gamma_sens)
colnames(a) = c('alpha',"gamma")
a = cbind(baseline %>% select(-c('alpha', 'gamma', 'spec', 'transformation'))%>% slice(rep(1:n(), each = nrow(a))), a)
a = a %>% mutate(spec = 'alpha and gamma', 
                 transformation = paste(alpha,' and ', gamma))
params_sensitivity = rbind(params_sensitivity, a)


rm(a)
print(paste0('There are ', nrow(params_sensitivity)," combinations to test" ))
```


## C. Define function to run model

In this section, I have not yet perfected the outputs of the models. I think it might be good to keep it like that, and then to define a second function to track the equilibrium outputs. So far, the functions return the equilibrium values of the stock. A second module (maybe tomorrow) will compute : 

* Equilibrium farmed and harvested quantities
* Prices paid to poachers
* Profits


```{r}
run_model = function(){
  # Function to run the model simulation
  # 0. Define growth = 
  growth = function(x){
    y = r*x*(1-x/k)
    return(y)
  }
  
  # 1. Run monopoly
  qty_monop = function(x){
    y = ((alpha - c)*sigma^2 * x^2) / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
  }
  # Store results
  result1 = data.frame( x = seq(1, k))%>%
    mutate(growth = growth(x),
           qty_monop = qty_monop(x))
  # 2. Run Cournot
  alpha_w = alpha
  alpha_f = alpha
  beta_w = beta
  beta_f = beta

  q_cournot_wild_own = function(x){
    y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W +     (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
    return(y)
  }
  result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x))
  
  # Run Betrand : 
  e   = gamma/(beta_w*beta_f - (gamma^2))
  a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
  a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
  b_f = beta_f/(beta_w*beta_f - (gamma^2))
  b_w = beta_w/(beta_w*beta_f - (gamma^2))
  
  q_b_own = function(x){
    y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
    return(y)
  }
  

  
  result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x))
  
  # Find steady states : 
  
  result1 = result1 %>% mutate(ss_monop = growth - qty_monop,
                               ss_cournot = growth - q_cournot_harvest,
                               ss_bertrand = growth - q_bertrand_harvest)
  steady_states = c()
  harvests = c()
  for(variable in c('ss_monop', 'ss_cournot', 'ss_bertrand')){
    # Comment that
    ss = which(sign(eval(parse(text = paste0('result1$',variable)))) != lag(sign(eval(parse(text = paste0('result1$', variable))))))
    
    if(length(ss)==1){
      steady_states = append(steady_states, c(result1[ss, 1], 
                                              NA,
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    NA, 
                                    NA))
    }
    else if(length(ss)==2){
      steady_states = append(steady_states, c(result1[ss[1], 1], 
                                              result1[ss[2], 1],
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    NA))
    }
    else if(length(ss)==3){
      steady_states = append(steady_states, c(result1[ss[1],1], 
                                              result1[ss[2],1],
                                              result1[ss[3],1]))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    growth(ss[3])))
    }
    else if(length(ss)==0){
      steady_states = append(steady_states, c(NA, NA, NA))
      harvests = append(harvests, c(NA, NA, NA))
    }
    
  }
  # Results : 
  results = append(append(params,
                   steady_states),
                   harvests)
  
  return(results)
}


run_model_ss = function(){
  # Function to run the model simulation
  # 0. Define growth = 
  growth = function(x){
    y = r*x*(1-x/k)
    return(y)
  }
  
  # 1. Run monopoly
  qty_monop = function(x){
    y = ((alpha - c)*sigma^2 * x^2) / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
  }
  # Store results
  result1 = data.frame( x = seq(1, k))%>%
    mutate(growth = growth(x),
           qty_monop = qty_monop(x))
  # 2. Run Cournot
  alpha_w = alpha
  alpha_f = alpha
  beta_w = beta
  beta_f = beta

  q_cournot_wild_own = function(x){
    y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W +     (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
    return(y)
  }
  result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x))
  
  # Run Betrand : 
  e   = gamma/(beta_w*beta_f - (gamma^2))
  a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
  a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
  b_f = beta_f/(beta_w*beta_f - (gamma^2))
  b_w = beta_w/(beta_w*beta_f - (gamma^2))
  
  q_b_own = function(x){
    y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
    return(y)
  }
  

  
  result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x))
  
  # Find steady states : 
  
  result1 = result1 %>% mutate(ss_monop = growth - qty_monop,
                               ss_cournot = growth - q_cournot_harvest,
                               ss_bertrand = growth - q_bertrand_harvest)
  steady_states = c()
  for(variable in c('ss_monop', 'ss_cournot', 'ss_bertrand')){
    # Comment that
    ss = which(sign(eval(parse(text = paste0('result1$',variable)))) != lag(sign(eval(parse(text = paste0('result1$', variable))))))
    
    if(length(ss)==1){
      steady_states = append(steady_states, c(result1[ss, 1], 
                                              NA,
                                              NA))
    }
    else if(length(ss)==2){
      steady_states = append(steady_states, c(result1[ss[1], 1], 
                                              result1[ss[2], 1],
                                              NA))

    }
    else if(length(ss)==3){
      steady_states = append(steady_states, c(result1[ss[1],1], 
                                              result1[ss[2],1],
                                              result1[ss[3],1]))

    }
    else if(length(ss)==0){
      steady_states = append(steady_states, c(NA, NA, NA))
    }
    
  }
  # Results : 
  results = append(params,
                   steady_states)
  
  return(results)
}


#Define parallelized version
run_model_par = function(params){
  
  k     = params[1]
  sigma = params[2]
  W     = params[3]
  beta  = params[4]
  v     = params[6]
  c     = params[7]
  alpha = params[8]
  r     = params[9]
  gamma = params[10]

  # Function to run the model simulation
  # 0. Define growth = 
  growth = function(x){
    y = r*x*(1-x/k)
    return(y)
  }
  
  # 1. Run monopoly
  qty_monop = function(x){
    y = (alpha - c)*sigma^2 * x^2 / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
  }
  # Store results
  result1 = data.frame(x = seq(1, k))%>%
    mutate(growth = growth(x),
           qty_monop = qty_monop(x),
           differ = growth - qty_monop)
  # 2. Run Cournot
  alpha_w = alpha
  alpha_f = alpha
  beta_w = beta
  beta_f = beta

  q_cournot_wild_own = function(x){
    y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W +     (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
    return(y)
  }
  
  s_c_own = function(x){
    y = (2*W*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/((sigma^2)*(x^2)*(4*beta_f*beta_w - gamma^2) + 4*beta_f*W)
    return(y)
  }
  q_farmed_cournot = function(s){
    y = (2 * beta_w * (alpha_f - v) - gamma* (alpha_w - (s + c)) )/(4*beta_w*beta_f - gamma^2)
    return(y)
  }
  
  result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x),
                               q_cournot_farmed = q_farmed_cournot(s_c_own(x)))
  
  # Run Betrand : 
  e   = gamma/(beta_w*beta_f - (gamma^2))
  a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
  a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
  b_f = beta_f/(beta_w*beta_f - (gamma^2))
  b_w = beta_w/(beta_w*beta_f - (gamma^2))
  
  s_b_own = function(x){
    y = (2*W*b_w*( b_f*(2*a_w + e*v) + c*((e^2) - 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_f*b_w - (e^2)) + 2*W*b_w*(2*b_w*b_f - (e^2)))
    return(y)
  }
  
  q_b_own = function(x){
    y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
    return(y)
  }
  
  quantity_farmed = function(s){
    y = b_f *(2*b_w*a_f + v*(e^2 - 2*b_w*b_f) + e*(a_w + (s+c)*b_w))/(4*b_f*b_w - e^2)
    return(y)
  }
  
  result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x),
                               q_bertrand_farmed = quantity_farmed(s_b_own(x)))
  
  # Find steady states : 
  result1 = result1 %>% mutate(ss_monop = growth - qty_monop,
                               ss_cournot = growth - q_cournot_harvest,
                               ss_bertrand = growth - q_bertrand_harvest)
  steady_states = c()
  harvests = c()
  for(variable in c('ss_monop', 'ss_cournot', 'ss_bertrand')){
    # Comment that
    ss = which(sign(eval(parse(text = paste0('result1$',variable)))) != lag(sign(eval(parse(text = paste0('result1$', variable))))))
    
    if(length(ss)==1){
      steady_states = append(steady_states, c(result1[ss, 1], 
                                              NA,
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    NA, 
                                    NA))
    }else if(length(ss)==2){
      steady_states = append(steady_states, c(result1[ss[1], 1], 
                                              result1[ss[2], 1],
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    NA))
    }else if(length(ss)==3){
      steady_states = append(steady_states, c(result1[ss[1],1], 
                                              result1[ss[2],1],
                                              result1[ss[3],1]))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    growth(ss[3])))
    }else if(length(ss)==0){
      steady_states = append(steady_states, c(NA, NA, NA))
      harvests = append(harvests, c(NA, NA, NA))
    }
    
  }
  
  # Find harvests : 

  # Compute prices : 
  
  # Compute profits :
  
  
  return(append(params,steady_states, harvests))
}
```


## D. Run

Two ways : 

* If `params_sensitivity` is not too large (less than 10,000 rows), can run it on the computer, it's easy

* If too long, use multiprocessing to perform analysis. I define chunks and then let the code run on the chunks of data. To run the model, define `r run_ = T`, otherwise leave it as is, and load the data. `

To deal with data, there are two layers : 

* Column `spec` displays which variable has been tweaked. For example, if one wants to analyze data for changed values of `v`, run `store %>% subset(spec == 'v')`, or when $c$ and $v$ move at the same time, `store %>% subset(spec == 'c and v')`.

* Second, column `transformation` can be used to color the graphs. If you want to check what how different values of `v` may impact the results, you can subset based on `transformation`. To find where each was applied, check section B's code

```{r}
run_ = T

if(file.exists(here('data', 'outputs', 'sensitivity_analysis.csv'))){
  run_ = F
}

if(run_==T){
  # No need for parallel computing with small dataset
  if(nrow(params_sensitivity)<10000){
    
    to_assign = colnames(params_sensitivity)
    to_assign = to_assign[1:9]
    store = data.frame()
    
    # Loop over all rows
    for(row in 1:nrow(params_sensitivity)){
      
      # First, assign environment variable
      for(variable in to_assign){
        assign(variable, 
               params_sensitivity[row,] %>% 
                 select(all_of(variable)) %>% 
                 pull())
      }
      # Then store data : 
      params = params_sensitivity[row,]%>%
        unlist()
      
      store = rbind(store, 
                    run_model_ss())
    }
    rm(alpha, beta, W, c, v, gamma)
    # Get names
    colnames(store) = append(colnames(params_sensitivity), 
                             c('ss_monop1', "ss_monop2", "ss_monop3", 'ss_cournot1',
                               'ss_cournot2', 'ss_cournot3', 'ss_bertrand1', "ss_bertrand2", 
                               'ss_bertrand3'))
                               #'harvest_monop1'
                               #'harvest_monop2',
                               #'harvest_monop3', 'harvest_cournot1','harvest_cournot2',
                               #'harvest_cournot3', 'harvest_bertrand1', 'harvest_bertrand2',
                               #'harvest_bertrand3'
    store['spec'] = as.factor(store$spec)
    store['transformation'] = as.factor(store$transformation)
    store = store %>% mutate_if(is.character, as.numeric)
    # Now that all the steady states stock and harvest rates are computed, do a big mutate for other output variables
    # i. Define output functions : 
    ### a. Monopoly ####
    qty_monop            = function(x, alpha, beta, c, W){
      y = ((alpha - c)*sigma^2 * x^2) / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
    }
    price_monop          = function(h, alpha, beta){
      y = alpha - beta*h
      return(y)
    }
    price_poachers_monop = function(x, alpha, beta, sigma, c, W){
      y = (alpha - c)*W/(beta*sigma^2*x^2 + W)
      return(y)
    }
    profit_monop         = function(h,x,alpha, beta, sigma, c, W){
      y = price_monop(h, alpha, beta)*h - (c + price_poachers_monop(x, alpha, beta, sigma, c, W))*h
      return(y)
    }
    # test
    store = store %>% mutate(harvest_monop1        = qty_monop(ss_monop1, alpha, beta, c, W),
                             harvest_monop2        = qty_monop(ss_monop2, alpha, beta, c, W),
                             harvest_monop3        = qty_monop(ss_monop3, alpha, beta, c, W),
                             price_monop1          = price_monop(harvest_monop1, alpha, beta),
                             price_monop2          = price_monop(harvest_monop2, alpha, beta),
                             price_monop3          = price_monop(harvest_monop3, alpha, beta),
                             price_poachers_monop1 = price_poachers_monop(ss_monop1, alpha, beta, sigma, c, W),
                             price_poachers_monop2 = price_poachers_monop(ss_monop2, alpha, beta, sigma, c, W),
                             price_poachers_monop3 = price_poachers_monop(ss_monop3, alpha, beta, sigma, c, W),
                             profit_monop1         = profit_monop(harvest_monop1,ss_monop1,alpha, beta, sigma, c, W),
                             profit_monop2         = profit_monop(harvest_monop2,ss_monop2,alpha, beta, sigma, c, W),
                             profit_monop3         = profit_monop(harvest_monop3,ss_monop3,alpha, beta, sigma, c, W))
    ### b. Cournot ####
    q_cournot        = function(x, alpha, beta, c, gamma, v, W){
      y = ((sigma^2)*(x^2)*(2*beta*(alpha - c) - gamma*(alpha - v)))/(4*beta*W + (sigma^2)*(x^2)*(4*beta*beta - (gamma^2)))
    return(y)
    }

    s_c_own          = function(x, alpha, beta, gamma, sigma, c, W, v){
      y = (2*W*(2*beta*(alpha - c) - gamma*(alpha - v)))/((sigma^2)*(x^2)*(4*beta*beta - gamma^2) + 4*beta*W)
      return(y)
    }
    q_farmed_cournot = function(s, alpha, beta, gamma, c, v){
      y = (2 * beta * (alpha - v) - gamma* (alpha - (s + c)) )/(4*beta*beta - gamma^2)
      return(y)
    }
    profit_farm      = function(hf, hw, alpha, beta, gamma, v){
      y = (alpha - beta*hf - gamma*hw - v)*hf
      return(y)
    }
    profit_trader    = function(hf, hw, x, alpha, beta, gamma, c, W, v){
      y = (alpha - beta*hw - gamma*hf - s_c_own(x, alpha, beta, gamma, sigma, c, W, v) - c)*hw
      return(y)
    }
    price_farmed     = function(alpha, beta, gamma, hw, hf){
      y = alpha - beta*hf - gamma*hf
      return(y)
    }
    price_wild       = function(alpha, beta, gamma, hw, hf){
      y = alpha - beta*hw - gamma*hf
      return(y)
    }
    
    store = store %>% mutate(harvest_cournot1        = q_cournot(ss_cournot1, alpha, beta, c, gamma, v, W),
                             price_poachers_cournot1 = s_c_own(ss_cournot1, alpha, beta, gamma, sigma, c, W, v),
                             farmed_cournot1         = q_farmed_cournot(price_poachers_cournot1,alpha, beta, gamma, c, v),
                             p_farmed_cournot1       = price_farmed(alpha, beta, gamma, harvest_cournot1, farmed_cournot1),
                             p_wild_cournot1         = price_wild(alpha, beta, gamma, harvest_cournot1, farmed_cournot1),
                             profit_farmed_cournot1  = profit_farm(farmed_cournot1, harvest_cournot1, alpha, beta, gamma, v),
                             profit_trader_cournot1  = profit_trader(farmed_cournot1, harvest_cournot1, ss_cournot1, alpha, beta, gamma, c, W, v),
                            # Second steady state                        
                             harvest_cournot2        = q_cournot(ss_cournot2, alpha, beta, c, gamma, v, W),
                             price_poachers_cournot2 = s_c_own(ss_cournot2, alpha, beta, gamma, sigma, c, W, v),
                             farmed_cournot2         = q_farmed_cournot(price_poachers_cournot2,alpha, beta, gamma, c, v),
                             p_farmed_cournot2       = price_farmed(alpha, beta, gamma, harvest_cournot2, farmed_cournot2),
                             p_wild_cournot2         = price_wild(alpha, beta, gamma, harvest_cournot2, farmed_cournot2),
                             profit_farmed_cournot2  = profit_farm(farmed_cournot2, harvest_cournot2, alpha, beta, gamma, v),
                             profit_trader_cournot2  = profit_trader(farmed_cournot2, harvest_cournot2, ss_cournot2, alpha, beta, gamma, c, W, v),
                            # Third steady state     
                             harvest_cournot3        = q_cournot(ss_cournot3, alpha, beta, c, gamma, v, W),
                             price_poachers_cournot3 = s_c_own(ss_cournot3, alpha, beta, gamma, sigma, c, W, v),
                             farmed_cournot3         = q_farmed_cournot(price_poachers_cournot3,alpha, beta, gamma, c, v),
                             p_farmed_cournot3       = price_farmed(alpha, beta, gamma, harvest_cournot3, farmed_cournot3),
                             p_wild_cournot3         = price_wild(alpha, beta, gamma, harvest_cournot3, farmed_cournot3),
                             profit_farmed_cournot3  = profit_farm(farmed_cournot3, harvest_cournot3, alpha, beta, gamma, v),
                             profit_trader_cournot3  = profit_trader(farmed_cournot3, harvest_cournot3, ss_cournot3, alpha, beta, gamma, c, W, v))
    # Bertrand
    store = store %>% mutate(e   = gamma/(beta*beta - (gamma^2)),
                             a_f = (alpha*beta - alpha*gamma)/(beta*beta - (gamma^2)),
                             a_w = (alpha*beta - alpha*gamma)/(beta*beta - (gamma^2)),
                             b_f = beta/(beta*beta - (gamma^2)),
                             b_w = beta/(beta*beta - (gamma^2)))
  q_bertrand       = function(x,v,c, a_f, a_w, b_f, b_w, e,W){
      y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
  return(y)
  }
  
  s_b_own          = function(x, a_f, a_w, b_f, b_w, e, W, c, v){
    y = (2*W*b_w*( b_f*(2*a_w + e*v) + c*((e^2) - 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_f*b_w - (e^2)) + 2*W*b_w*(2*b_w*b_f - (e^2)))
    return(y)
  }
  quantity_farmed  = function(s, a_f, a_w, b_f, b_w, e, W, c, v){
    y = b_f *(2*b_w*a_f + v*(e^2 - 2*b_w*b_f) + e*(a_w + (s+c)*b_w))/(4*b_f*b_w - e^2)
    return(y)
  }
  price_farmed     = function(s, a_f, a_w, b_f, b_w, e, c, v){
    y = (2*b_w*(a_f + v*b_f) + e*(a_w + b_w*(s+c)))/(4*b_f*b_w - e^2)
    return(y)
  }
  price_trader     = function(s, a_f, a_w, b_f, b_w, e, c, v){
    y = (2*b_f *(a_w+b_w*(s+c))+e*(a_f +v*b_f))/(4*b_f*b_w - e^2)
    return(y)
  }
  profit_farm      = function(pw, pf, a_f, b_f, e, v){
    y = (pf - v)*(a_f - b_f*pf + e*pw)
    return(y)
  }
  profit_trader    = function(pw, pf, a_w, b_w, e, s, c){
    y = (pw - s - c)*(a_w - b_w*pw + e*pf)
    return(y)
  }
    
  store = store %>% mutate(harvest_bertrand1        = q_bertrand(ss_bertrand1,v,c, a_f, a_w, b_f, b_w, e,W),
                           price_poachers_bertrand1 = s_b_own(ss_bertrand1, a_f, a_w, b_f, b_w, e, W, c, v),
                           farmed_bertrand1         = quantity_farmed(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, W, c, v),
                           p_farmed_bertrand1       = price_farmed(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, c, v),
                           p_wild_bertrand1         = price_trader(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, c, v),
                           profit_farmed_bertrand1  = profit_farm(p_wild_bertrand1, p_farmed_bertrand1, a_f, b_f, e, v),
                           profit_trader_bertrand1  = profit_trader(p_wild_bertrand1, p_farmed_bertrand1, a_w, b_w, e, price_poachers_bertrand1, c),
                           # Second steady state:
                           harvest_bertrand2        = q_bertrand(ss_bertrand2,v,c, a_f, a_w, b_f, b_w, e,W),
                           price_poachers_bertrand2 = s_b_own(ss_bertrand2, a_f, a_w, b_f, b_w, e, W, c, v),
                           farmed_bertrand2         = quantity_farmed(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, W, c, v),
                           p_farmed_bertrand2       = price_farmed(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, c, v),
                           p_wild_bertrand2         = price_trader(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, c, v),
                           profit_farmed_bertrand2  = profit_farm(p_wild_bertrand2, p_farmed_bertrand2, a_f, b_f, e, v),
                           profit_trader_bertrand2  = profit_trader(p_wild_bertrand2, p_farmed_bertrand2, a_w, b_w, e, price_poachers_bertrand2, c),
                           #Third steady state : 
                           harvest_bertrand3        = q_bertrand(ss_bertrand3,v,c, a_f, a_w, b_f, b_w, e,W),
                           price_poachers_bertrand3 = s_b_own(ss_bertrand3, a_f, a_w, b_f, b_w, e, W, c, v),
                           farmed_bertrand3         = quantity_farmed(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, W, c, v),
                           p_farmed_bertrand3       = price_farmed(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, c, v),
                           p_wild_bertrand3         = price_trader(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, c, v),
                           profit_farmed_bertrand3  = profit_farm(p_wild_bertrand3, p_farmed_bertrand3, a_f, b_f, e, v),
                           profit_trader_bertrand3  = profit_trader(p_wild_bertrand3, p_farmed_bertrand3, a_w, b_w, e, price_poachers_bertrand3, c))
  
    store['transformation'] = as.character(store$transformation)
  
    write.csv(store, here('data', 'outputs', 'sensitivity_analysis.csv'), row.names = F)

    }
  else{
    numcores = detectCores() - 4
# Set up storage
    store = data.frame()

# Set up the width of each run
    width = nrow(params_sensitivity)
    number_op = nrow(params_sensitivity)/width

# Loop over several runs is faster than 1 big run
    for (x in 1:number_op){
    # Make clusters
      cl = makeCluster(numcores)
    # Load tidyverse : otherwise, pipe operator is not recognized
      clusterEvalQ(cl,  library(tidyverse))

    # Start timer
      start = Sys.time()
    # Apply function accross nodes with a slice of the data of lenght width
      a = parApply(cl, 
                   params_sensitivity[width*(x-1)+1:width*x,],
                   1,
                   run_model_par)
      print(Sys.time() - start)

      a = as.data.frame(a)

      store = rbind(store, t(a))
    }
    colnames(store) = c('k', 'sigma', 'W', 'beta', 
                        'gamma_primitive', 'v', 'c', 
                        'alpha', 'r', 'gamma','ss_monop1', 'ss_monop2', 'ss_monop3',
                        'ss_cournot1', 'ss_cournot2', 'ss_cournot3', 'ss_bertrand1', 
                        'ss_bertrand2', 'ss_bertrand3')
  
    write.csv(store, here('data', 'outputs', 'sensitivity_analysis.csv'), row.names = F)}
}else{
  store = read.csv(here('data', 'outputs', 'sensitivity_analysis.csv'))
}

to_assign = colnames(params_sensitivity)
to_assign = to_assign[1:9]
# Reassign variables properly
for(variable in to_assign){
        assign(variable, 
               params_sensitivity[1,] %>% 
                 select(all_of(variable)) %>% 
                 pull())
}


```




# Sensitivity graphs

```{r}
# Define grid of colours
store = as.data.frame(read.csv(here('data', 'outputs', 'sensitivity_analysis.csv')))

low = 'red'
mid = 'white'
high = 'springgreen2'



# Set data to long format
to_keep = c('c', 'v', 'ss_monop1', 'ss_cournot1','ss_bertrand1')
df_cv = store %>% 
  subset(spec == 'c and v')%>% 
  select(all_of(to_keep))%>%
  drop_na()%>%
  mutate(ss_cournot_norm = (ss_cournot1 - ss_monop1)/ss_monop1*100,
         ss_bertrand_norm = (ss_bertrand1 - ss_monop1)/ss_monop1*100,)

df_cv = df_cv %>% pivot_longer(cols = !c('c','v'),
                               names_to = 'output',
                               values_to = 'value')

# Rename output for nice columns in the facet graph
output2 = function(x){
  if(x =='ss_cournot_norm'){
    return('Cournot steady state - normalized')
  }else if(x == 'ss_bertrand_norm'){
    return('Bertrand steady state - normalized')
  }
}

# Initial equilibrium data points
init_eq_m = store %>% subset(spec == 'baseline') %>% select(ss_monop1)%>%pull()
init_eq_b =  store %>% subset(spec == 'baseline') %>% select(ss_bertrand1)%>%pull()
init_eq_c =  store %>% subset(spec == 'baseline') %>% select(ss_cournot1)%>%pull()
init_eq = data.frame(c=c(c,c), v=c(v,v), value = c(init_eq_c/init_eq_m,
                                                   init_eq_b/init_eq_m))
# What we believe is fair for actual c
new_c = data.frame(c=c(4*c,4*c), v=c(v,v), value = c(1, 1))
# Impact of policy outcome if we subsidize v by 1000 per ton
new_v = data.frame(c=c(3*c,3*c), v=c(v-10000,v-10000), value = c(1, 1))


p = df_cv %>%
  subset(output %in% c('ss_cournot_norm', 'ss_bertrand_norm'))%>%
  mutate(output2 = sapply(output,output2))%>%
  ggplot(aes(x = c, y = v, fill = value))+
  geom_tile()+
  #scale_fill_distiller(type = 'div',
  #                     palette = 'RdYlGn',
  #                     direction = 1, 
  #                     name = '% change')+
  #scale_fill_gradient2(low = low, 
  #                     mid = mid,
  #                     high = high)+
  scale_fill_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")))+
  facet_grid(.~ output2)+
  theme_bw()+
  theme(legend.position = 'bottom')+
  ylab('Unit cost of farming ($USD/ton)')+
  xlab('Unit cost of transaction for traders ($USD/ton)')+
  guides(colour = guide_legend(title.position = "top"))

p + 
  labs(fill = '% change compared to steady state monopoly')+
  geom_point(data = init_eq, col = 'black', shape=4)
ggsave(here('visuals', 'Figure5.jpg'))
#  geom_point(data = new_c, col = 'grey')
#  geom_point(data = new_v, col = 'blue')

```

```{r, Bertrand outcome with c and v}

store = as.data.frame(read.csv(here('data', 'outputs', 'sensitivity_analysis.csv')))

# Set data to long format
to_keep = c('c', 'v', 'price_poachers_cournot1', 'price_poachers_bertrand1', 'ss_monop1', 'ss_cournot1', 'ss_bertrand1')

df_cv = store %>% 
  subset(spec == 'c and v')%>% 
  select(all_of(to_keep))%>%
  drop_na()

df_cv1 = df_cv %>%
  mutate(ss_bertrand_norm = (ss_bertrand1-ss_monop1)/ss_monop1*100,
         c_ = cut(c,10), 
         v_ = cut(v,5))

levels(df_cv1$c_) = c('0 - 1,490',
                      '1,490 - 2,980',
                      '2,980-4,470',
                      '4,470 - 5,960', 
                      '5,960 - 7,450', 
                      '7,450 - 8,940', 
                      '8,940 - 10,400',
                      '10,400 - 11,900',
                      '11,900 - 13,400',
                      '13,400 - 14,900')
levels(df_cv1$v_) = c('6,610 $ - 25,500 $',
                      '25,500 $ - 44,200 $',
                      '44,200 $ - 63,000 $', 
                      '63,000 $ - 81,800 $', 
                      '81,800 $ - 101,500 $')

font_ = 'AppleGothic'
custom_breaks = c(0, 5000, 10000, 14900)
df_cv1 %>%
  ggplot(aes(x = price_poachers_bertrand1+c,
             y = ss_bertrand_norm))+
  geom_line(aes(color = c))+
  geom_hline(aes(yintercept=0), linetype=2)+
  facet_grid(.~v_)+
  #scale_color_viridis_c()+
  #scale_color_brewer(palette = 'YlOrRd')+
  scale_color_gradient(low = "gold1", 
                       high = "firebrick3", 
                       breaks = custom_breaks,
                       labels = custom_breaks, 
                       limits = c(0, 14900))+
  #scale_color_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")))+
  ylab('Variation from initial equilibrium (in %)')+
  xlab('Cost for traders (price paid and transaction cost) in USD')+
  labs(color = 'Cost of \ntransaction \n(in USD)')+
  labs(title = 'Normalized steady states in price setting scenario',
       subtitle = 'With binned farming costs')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 60,
                                   hjust = 1),
        legend.position = "right",
        strip.text.x  = element_text(family = font_) ,
        axis.title.x  = element_text(family = font_),
        axis.text = element_text(family = font_),
        axis.title.y  = element_text(family = font_),
        legend.text = element_text(family = font_), 
        legend.title = element_text(family = font_),
        legend.key.width = unit(.3, "cm"),
        legend.key.height = unit(1, 'cm'),
        plot.title = element_text(family= font_,),
        plot.subtitle = element_text(family=font_))

ggsave(here('visuals', 'Figure5b.jpg'), width = 10, height = 8)

```

```{r, Cournot outcome with c and v}

store = as.data.frame(read.csv(here('data', 'outputs', 'sensitivity_analysis.csv')))

# Set data to long format
to_keep = c('c', 'v', 'price_poachers_cournot1', 'price_poachers_bertrand1', 'ss_monop1', 'ss_cournot1', 'ss_bertrand1')

df_cv = store %>% 
  subset(spec == 'c and v')%>% 
  select(all_of(to_keep))%>%
  drop_na()

df_cv1 = df_cv %>%
  mutate(ss_cournot_norm = (ss_cournot1-ss_monop1)/ss_monop1*100,
         c_ = cut(c,10), 
         v_ = cut(v,5))

levels(df_cv1$c_) = c('0 - 1,490',
                      '1,490 - 2,980',
                      '2,980-4,470',
                      '4,470 - 5,960', 
                      '5,960 - 7,450', 
                      '7,450 - 8,940', 
                      '8,940 - 10,400',
                      '10,400 - 11,900',
                      '11,900 - 13,400',
                      '13,400 - 14,900')
levels(df_cv1$v_) = c('6,610 $- 25,500 $',
                      '25,500 $ - 44,200 $',
                      '44,200 $ - 63,000 $', 
                      '63,000 $ - 81,800 $', 
                      '81,800 $ - 101,500 $')

font_ = 'AppleGothic'
custom_breaks = c(0, 5000, 10000, 14900)
df_cv1 %>%
  ggplot(aes(x = price_poachers_cournot1+c,
             y = ss_cournot_norm))+
  geom_line(aes(color = c))+
  geom_hline(aes(yintercept=0), linetype=2)+
  facet_grid(.~v_)+
  #scale_color_viridis_c()+
  #scale_color_brewer(palette = 'YlOrRd')+
  scale_color_gradient(low = "gold1", 
                       high = "firebrick3", 
                       breaks = custom_breaks,
                       labels = custom_breaks, 
                       limits = c(0, 14900))+
  #scale_color_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")))+
  ylab('Variation from initial equilibrium (in %)')+
  xlab('Cost for traders (price paid and transaction cost) in USD')+
  labs(color = 'Cost of \ntransaction \n(in USD)')+
  labs(title = 'Normalized steady states in quantity adjustment scenario',
       subtitle = 'With binned farming costs')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 60,
                                   hjust = 1),
        legend.position = "right",
        strip.text.x  = element_text(family = font_) ,
        axis.title.x  = element_text(family = font_),
        axis.text = element_text(family = font_),
        axis.title.y  = element_text(family = font_),
        legend.text = element_text(family = font_), 
        legend.title = element_text(family = font_),
        legend.key.width = unit(.3, "cm"),
        legend.key.height = unit(1, 'cm'),
        plot.title = element_text(family= font_,),
        plot.subtitle = element_text(family=font_))

ggsave(here('visuals', 'Figure5c.jpg'), width = 10, height = 8)
 #  geom_point(data = new_c, col = 'grey')
#  geom_point(data = new_v, col = 'blue')
```


```{r, c & v & gamma and equilibria}
to_keep = c('c', 'v','gamma', 'ss_monop1', 'ss_cournot1','ss_bertrand1')
df_cv = store %>% 
  subset(spec == 'c and v and gamma')

summary(df_cv$ss_monop2)
summary(df_cv$ss_bertrand2)

df_cv  = df_cv %>% 
  select(all_of(to_keep))%>%
  drop_na()%>%
  mutate(ss_cournot_norm = (ss_cournot1 - ss_monop1)/ss_monop1*100,
         ss_bertrand_norm = (ss_bertrand1 - ss_monop1)/ss_monop1*100)

df_cv = df_cv %>% pivot_longer(cols = !c('c','v','gamma'),
                               names_to = 'output',
                               values_to = 'value')


df_cv %>%
  mutate(gamma_rel = paste(round(gamma/beta*100,2), '%'))%>%
  subset(output %in% c('ss_cournot_norm', 'ss_bertrand_norm'))%>%
  mutate(output2 = sapply(output,output2))%>%
  ggplot(aes(x = c, y = v, fill = value))+
  geom_tile()+
  #scale_fill_gradient2(low = low, 
  #                     mid = mid,
  #                     high = high)+
  scale_fill_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")))+
  facet_grid(vars(gamma_rel),vars(output2))+
  theme_bw()+
  theme(legend.position = 'bottom')+
  guides(colour = guide_legend(title.position = "top"))+
  labs(fill = '% change compared to steady state monopoly')

ggsave(here('visuals/supplementary_visuals', 'Figure6.jpg'))

```

## Other analysis

1. What demand increase would be needed to offset the positive effects of competition?

2. How do results evolve with substitutability?

```{r}
Latex = T

ss_mon = store %>% subset(spec == 'baseline') %>% select(ss_monop1) %>% pull()


checker = store %>%
  subset(spec %in% c('baseline', 'gamma'))%>%
  mutate(`Cournot normalized` = paste0(round((ss_cournot1/ss_mon - 1)*100,2), '%'),
         `Bertrand normalized` = paste0(round((ss_bertrand1/ss_mon -1)*100,2), '%'))%>%
  select(gamma, transformation, `Cournot normalized`, `Bertrand normalized`)%>%
  mutate(transformation = paste0(round(as.numeric(gamma)/beta*100,2), '%'), 
         gamma = round(gamma, 2))%>%
  arrange(transformation)

kable(checker)
if(Latex==T){
  checker %>%
  kable(caption = 'Evolution of steady states with $gamma$', 
        format = 'latex', 
        align = 'c')
}
```

```{r, graph}
output3 = function(x){
  if(x %in% c('ss_monop1', 'ss_monop2', 'ss_monop3')){
    return('Vertical monopoly')
  }else if(x %in% c('ss_cournot1', 'ss_cournot2', 'ss_cournot3')){
    return('Qty adjustment')
  }else if(x %in% c('ss_bertrand1', 'ss_bertrand2', 'ss_bertrand3')){
    return('Price setting')
  }
}

output4 = function(x){
  x = as.integer(x)
  if(x<=30){
    return('Low - 10%')
  }else if(x>30 & x<=65){
    return('Medium - 50%')
  }else if(x>65){
    return('Large - 90%')
  }
}

output5 = function(x){
  if(x > -55){
    return('Large')
  }else if(x < (-55) & x > (-80)){
    return('Middle')
  }else if(x < (-80)){
    return('Low')
  }else if(is.na(x)){
    return(NA)
  }
}

pal = c("mediumseagreen", "black", 'gold1', 'darkorange','orangered', 'firebrick3', 'brown', 'grey')
font_ = 'AppleGothic'

ss_mon = store %>% subset(spec == 'baseline') %>% select(ss_monop1) %>% pull()
checker = store %>% 
  subset(spec =='alpha and gamma')%>%
  select(alpha, gamma, ss_monop1, ss_monop2, ss_monop3, ss_cournot1, ss_cournot2, ss_cournot3,
         ss_bertrand1, ss_bertrand2, ss_bertrand3)%>%
  pivot_longer(cols = -c('alpha', 'gamma'), 
               names_to = 'names', 
               values_to = 'values')%>%
  mutate(names = sapply(names, output3), 
         alpha = as.numeric(alpha/calibration$value[which(calibration$params=='alpha')]), 
         gamma = round(gamma/calibration$value[which(calibration$params=='beta')],2)*100,
         values2 = (values/ss_mon - 1)*100)


checker$values3 = cut(checker$values2, breaks = c(30,-50,-86, -100), include.lowest=T)
checker$values4 = paste0(checker$values3, checker$alpha)

checker = checker %>%
  mutate(gamma = as.integer(gamma))%>%
  filter(gamma %in% c(10, 50, 90))%>%
  mutate(gamma = sapply(gamma, output4))%>%
  mutate(gamma = factor(gamma, levels = c('Low - 10%', 'Medium - 50%', 'Large - 90%')),
         alpha2 = factor((round(alpha,2)-1)*100))%>%
  drop_na()

levels(checker$alpha2) = c(levels(checker$alpha2), -50)
checker$alpha2[checker$names=='Vertical monopoly'] <- -50

checker %>%
  ggplot(aes(x = names, 
             y=values2, 
             colour = alpha2, 
             group = values4))+
  geom_point(size = 2)+
  #geom_line()+
  #geom_hline(yintercept = 10000, linetype='dotted')+
  #geom_hline(yintercept = 2450, linetype='dotted')+
  facet_wrap(vars(gamma))+
  scale_color_manual(values = pal, breaks = c("-20", "0", "20", "40", "60","80", "100"))+
  theme_bw()+
  geom_hline(yintercept = -43, linetype = 'dotted')+
  geom_hline(yintercept = -86, linetype = 'dotted')+
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'grey')+
  xlab(' ')+
  ylab('Deviation (in %) from vertical \nmonopoly equilibrium population')+
  scale_shape_manual(values = c(4, 17, 8))+
  labs(colour = 'Demand \nvariation (in %)')+
  guides(shape = 'none',
         color=guide_legend(nrow=4,byrow=F))+
  theme(axis.text.x = element_text(angle = 60,
                                   hjust = 1),
        legend.position = "right",
        strip.text.x  = element_text(family = font_) ,
        axis.title.x  = element_text(family = font_),
        axis.text = element_text(family = font_),
        axis.title.y  = element_text(family = font_, size = 9),
        legend.text = element_text(family = font_), 
        legend.title = element_text(family = font_), 
        aspect.ratio = 10/4)
ggsave(here('visuals', 'figure_unclear.jpg'), height = 11)

```
```{r, alternative proposal}
checker %>%
  subset(names != 'Vertical monopoly')%>%
  ggplot(aes(x = names, 
             y=values2, 
             colour = alpha2, 
             group = values4))+
  geom_point(size = 2)+
  #geom_line()+
  #geom_hline(yintercept = 10000, linetype='dotted')+
  #geom_hline(yintercept = 2450, linetype='dotted')+
  facet_wrap(vars(gamma))+
  scale_color_manual(values = pal)+
  theme_bw()+
  geom_hline(yintercept = -43, linetype = 'dotted')+
  geom_hline(yintercept = -86, linetype = 'dotted')+
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'grey')+
  xlab(' ')+
  ylab('Deviation (in %) from vertical \nmonopoly equilibrium population')+
  scale_shape_manual(values = c(4, 17, 8))+
  labs(colour = 'Demand \nvariation (in %)')+
  guides(shape = 'none',
         color=guide_legend(nrow=4,byrow=F))+
  theme(axis.text.x = element_text(angle = 60,
                                   hjust = 1),
        legend.position = "right",
        strip.text.x  = element_text(family = font_) ,
        axis.title.x  = element_text(family = font_),
        axis.text = element_text(family = font_),
        axis.title.y  = element_text(family = font_, size = 9),
        legend.text = element_text(family = font_), 
        legend.title = element_text(family = font_), 
        aspect.ratio = 10/4)
ggsave(here('visuals', 'figure_unclear_without_monopoly.jpg'), height = 11)


```

```{r, yet another idea}
# Remove the monopoly and gray out the intermediary equilibria.
checker = store %>% 
  subset(spec =='alpha and gamma')%>%
  select(alpha, gamma, ss_monop1, ss_monop2, ss_monop3, ss_cournot1, ss_cournot2, ss_cournot3,
         ss_bertrand1, ss_bertrand2, ss_bertrand3)%>%
  pivot_longer(cols = -c('alpha', 'gamma'), 
               names_to = 'names', 
               values_to = 'values')%>%
  mutate(names = sapply(names, output3), 
         alpha = as.numeric(alpha/calibration$value[which(calibration$params=='alpha')]), 
         gamma = round(gamma/calibration$value[which(calibration$params=='beta')],2)*100,
         values2 = (values/ss_mon - 1)*100, 
         gamma = as.integer(gamma))%>%
  filter(gamma %in% c(10, 50, 90))%>%
  mutate(gamma = sapply(gamma, output4))%>%
  mutate(gamma = factor(gamma, levels = c('Low - 10%', 'Medium - 50%', 'Large - 90%')),
         alpha2 = factor((round(alpha,2)-1)*100))%>%
  drop_na()


checker$values3 = cut(checker$values2, breaks = c(30,-50,-86, -100), include.lowest=T)
checker$values4 = paste0(checker$values3, checker$alpha)

levels(checker$alpha2) = c(levels(checker$alpha2), -50)
checker$alpha2[checker$names=='Vertical monopoly'] <- -50
checker$alpha2[checker$values3 == '(-86,-50]'] <- -50

# Graph itself
checker %>%
  subset(names != 'Vertical monopoly')%>%
  ggplot(aes(x = names, 
             y=values2, 
             colour = alpha2, 
             group = values4))+
  geom_point(size = 2)+
  #geom_line()+
  #geom_hline(yintercept = 10000, linetype='dotted')+
  #geom_hline(yintercept = 2450, linetype='dotted')+
  facet_wrap(vars(gamma))+
  scale_color_manual(values = pal, breaks = c("-20", "0", "20", "40", "60","80", "100"))+
  theme_bw()+
  geom_hline(yintercept = -43, linetype = 'dotted')+
  geom_hline(yintercept = -86, linetype = 'dotted')+
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'grey')+
  xlab(' ')+
  ylab('Deviation (in %) from vertical \nmonopoly equilibrium population')+
  scale_shape_manual(values = c(4, 17, 8))+
  labs(colour = 'Demand \nvariation (in %)')+
  guides(shape = 'none',
         color=guide_legend(nrow=4,byrow=F))+
  theme(axis.text.x = element_text(angle = 60,
                                   hjust = 1),
        legend.position = "right",
        strip.text.x  = element_text(family = font_) ,
        axis.title.x  = element_text(family = font_),
        axis.text = element_text(family = font_),
        axis.title.y  = element_text(family = font_, size = 9),
        legend.text = element_text(family = font_), 
        legend.title = element_text(family = font_), 
        aspect.ratio = 10/4)
ggsave(here('visuals', 'figure_unclear_last.jpg'), height = 11)
```
## Table for equilibria corresponding with above graph

```{r}
Latex = F
# Reinitiate data
checker = store %>% 
  subset(spec =='alpha and gamma')%>%
  select(alpha, gamma, ss_monop1, ss_monop2, ss_monop3, ss_cournot1, ss_cournot2, ss_cournot3,
         ss_bertrand1, ss_bertrand2, ss_bertrand3)%>%
  pivot_longer(cols = -c('alpha', 'gamma'), 
               names_to = 'names', 
               values_to = 'values')%>%
  mutate(names = sapply(names, output3), 
         alpha = as.numeric(alpha/calibration$value[which(calibration$params=='alpha')]), 
         gamma = round(gamma/calibration$value[which(calibration$params=='beta')],2)*100,
         values2 = (values/ss_mon - 1)*100, 
         gamma = as.integer(gamma))%>%
  drop_na()

# Set storage
storage = data.frame(0, 0, 0, 0, 0, 0)
thresh = c(0, 2450, 10000, 500000)
colnames(storage) = c("gamma",
                      "Vertical monopoly",
                      "Qty adjustment",
                      "Price setting",
                      "alpha",
                      "Equilibrium" )

for(x in c(1, 1.2, 1.4, 1.6, 1.8)){
  # Loop for all demand multipliers
  for( i in seq(1, length(thresh)-1)){
    # Loop over threshold values for different types of equilibria
    
    a = checker %>%
    filter(alpha < x+.05 & alpha > x - .05 )%>% # Filter with bandwidth otherwise does not match
    filter(values > thresh[i] & values < thresh[i+1])%>%
    select(-c(values))%>%
    drop_na()
    
    # If there are values in a certain type of equilibrium, export values in wide format
    if(nrow(a)>0){
    a = a %>%
    pivot_wider(names_from=names, 
                values_from = values2,
                values_fn = list)%>%
    subset(as.character(gamma) %in% c(10, 50, 90))%>%
    mutate(alpha = x)
      
    # Clean labeling of equilibria
    if(i == 1){
      a = a %>%
        mutate(Equilibrium = 'Low - stable')
    }else if (i == 2){
      a = a %>% 
        mutate(Equilibrium = 'Middle - unstable')
    }else if (i == 3){
      a = a %>%
        mutate(Equilibrium = 'High - stable')
    }
  storage = rbind(storage, a)
  }
}
}
# Formating of table
storage = storage[-1, c(5,1,6,2,3,4)]

storage = as.data.frame(storage) %>%
    replace(.=='NULL', NA)%>%
    mutate(gamma = paste0(gamma, '\ %'),
           `Vertical monopoly` = round(unlist(`Vertical monopoly`), 2), 
           `Qty adjustment` = round(unlist(`Qty adjustment`), 2), 
           `Price setting` = round(unlist(`Price setting`), 2))
  
  colnames(storage) = c('Demand mult. coef.', '$gamma$ (% of $beta$)','Equilibrium', 'Monopoly variation (in %)', 'Cournot variation (in %)', 'Betrand variation (in %)')
if(Latex == T){
  
  storage %>%
    kable(caption = 'Evolution of steady states (in % from baseline monopoly steady state)', 
          format  = 'latex',
          align = 'c', 
          row.names = F)
  
}else{
  storage %>%
    kable(caption = 'Evolution of steady states (in % from baseline monopoly steady state)', 
          format  = 'html',
          align = 'c', 
          row.names = F)
  
}
```

## Sensitivity analysis for $W$

```{r}
checker = store %>% 
  subset(spec =='W')%>%
  select(W, ss_monop1, ss_monop2, ss_monop3, ss_cournot1, ss_cournot2, ss_cournot3,
         ss_bertrand1, ss_bertrand2, ss_bertrand3)%>%
  pivot_longer(cols = -c('W'), 
               names_to = 'names', 
               values_to = 'values')%>%
  mutate(names = sapply(names, output3))%>%
  drop_na()

checker %>%
  ggplot(aes(x = W, y = values, colour = names, group = names))+
  geom_point()+
  geom_line()+
  theme_bw()+
  scale_color_aaas()
```

